Reviving stochasticity: eccentricity convergence depends on black hole binary orbit

### 2023-05-16 papers/paper-eccentricity/sections/numerical.tex
Orbit plot for paper
New parameter files for updated Hernquist runs

New organisation of plotting classes, with update to GradientPlot methods

\begin{figure*}
    \includegraphics{orbits}
    \caption{\drafting{Orbits of the different merger systems, colour coded according to the initial orbital eccentricity. Note that the duration shown for each orbit is not currently consistent: probably should cut the plot to when the binary semimajor axis reaches some set value}}
    \label{fig:orbits}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics{orbits}
    \caption{\drafting{Orbit of a SMBH in one of the e=0.99 mergers, which by symmetry of the equal mass system is the same as the second BH orbit reflected. Line coloured according to time. Point A shows a time just before the first hard scattering, and point B a time just after. The circle marker indicates the final position of the BH before the BHs become bound.}}
    \label{fig:orbit}
\end{figure*}
